Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-11 ms.tex
Putting back modified table

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ & {comments}\\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
10$^{6}$ & 300 & 0.8 & $>$XXX & $ 3.2 \times 10^{ -4 }$ & 4.7 & N & rb in fact
unresolved \\
10$^{6}$ & 600 & 0.8 & $>$XXX & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ & N & \\
10$^{6}$ & 1200 & 0.8 & $>$XXX & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  N &\\
10$^{7}$ & 300 & 0.8 & 100 & $ 2.5 \times 10^{ -3 }$ & 0.29 & N &\\
10$^{7}$ & 600 & 0.8 & 100 & $ 1.8 \times 10^{ -4 }$ & 97 &N  & \\
10$^{7}$ & 1200 & 0.8 & $>$ & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ & N & \\
\hline
10$^{8}$ & 300 & 0.8 & 100 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ & Y  & \\
10$^{8}$ & 600 & 0.8 & 100 & $ 7.3 \times 10^{ -4 }$ & 21 & N & \\
10$^{8}$ & 1200 & 0.8 & 100 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ & N &  \\
10$^{8}$ & 300 & 0.8 & 50 & $ 8.2 \times 10^{ -3 }$ & 0.19 & N & \\
10$^{8}$$\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & N & \\
10$^{8}$ & 300 & 0.8 & 200 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &Y & TI/convergence \\
%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
%  -3 }$ &  TI/convergence\\
10$^{8}$ & 300 & 0.8 & 400 &  &  & Y & TI/run unsuccessful\\
10$^{7}$ & 300 & 0.8 & 50 & $ 2.0 \times 10^{ -3 }$ & 0.46 & N &\\
10$^{7}$ & 300 & 0.8 & 200 & $ 5.3 \times 10^{ -3 }$ & 0.12 & Y & TI/convergence\\
%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
%10^{ -2 }$   & TI/convergence  \\
10$^{7}$ & 300 & 0.8 & 400 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
10^{ -2 }$ & Y &TI/convergence \\
10$^{6}$ & 1200 & 0.1 & U & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
10^{ 4 }$ & N & \\
10$^{7}$ & 1200 & 0.1 & U & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
  3 }$ & N & tried run w rb=100 pc resolved, what would happen if rb=400 pc?\\
10$^{6}$ & 1200 & 0.1 & 100 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &N  &\\
10$^{7}$ & 1200& 0.1 & 100 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &N&  \\
10$^{8}$ & 1200 & 0.1 & 100 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ & N& \\
10$^{8}$ & 1200 & 0.1 & 50 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &N  &\\
10$^{8}$ & 1200 & 0.1 & 200 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &N&  \\
%1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
10$^{8}$ & 1200 & 0.1 & 400 & $ 1.8 \times 10^{ -2 }$ & 0.37 & Y &TI/convergence\\
\hline
\label{table:models}  
\end{tabular}
$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in Eddington units, normalized to a stellar mass input parameter $\eta = 0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at stagnation radius.  $^{(e)}$ Is solution thermally unstable?  $\dagger$Calculated including radiative cooling, assuming $\eta = 0.04$.  {\bf BDM: (1) remove comments column, (2) update numbers assuming eta = 0.04, (3) make sure all combinations of vw and mbh are included}
\end{minipage}
\end{table*}

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
\hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  $^{(e)}$ Is solution thermally unstable?
$\dagger$Calculated including radiative cooling, assuming $\eta =
0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

\end{table*}
